Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-17 special-issue-ci/volunteer-clouds-ieee-ci-si.tex

\begin{abstract}
Volunteer computing is used routinely 
% (Paloma) Adverbs are always written before verbs, check this throughout the text
in science and industry, but it
still has a long way to go if it is going to become
% (Paloma) I would propose "a long way to go in order to become"
 a mainstream technology in
the same way the cloud technologies in general have. The lack of 
% (Paloma) Add "both" here to better complete the sentence
general
purpose and open source tools
with analytics built in
% (Paloma) "built-in" is an adjective and, as such, has to be written before names
 could be one of the reasons why this is so, as
well as the lack of proofs of concept. That is why in this paper we
present {\sf NodIO}, a framework used to create client-server architectures for distributed
evolutionary algorithms, written entirely % (Paloma) Adverb. I would also add an "and" after the comma
 in JavaScript, which needs
minimal server support to work and is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser.  The architecture, along with some initial results on the
expected performance and scaling
behavior, is presented. We also use the algorithm data to
find out what kind of patterns the user behavior follow and try to fit
them to some statistical distribution.
\end{abstract}

>>>>

\begin{abstract}
Volunteer computing is used routinely
% (Paloma) Adverbs are always written before verbs, check this throughout the text
 in science and industry, but it
still has a long way to go if it is going to become
% (Paloma) I would propose "a long way to go in order to become"
 a mainstream
technology in the same way the cloud technologies in general have. The
lack of % (Paloma) Add "both" here to better complete the sentence
general purpose and open source tools with analytics built in
% (Paloma) "built-in" is an adjective and, as such, has to be written before names
could be one of the reasons why this is so, as well as the lack of
proofs of concept. That is why in this paper we present {\sf NodIO}, a
framework used to create client-server architectures for distributed
evolutionary algorithms, written entirely % (Paloma) Adverb. I would also add an "and" after the comma
in JavaScript, which needs
minimal server support to work and is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser, as well as any other client consuming its REST application
programming interface.  The architecture, along with some initial
results on the expected performance and scaling behavior when the
number of users is increased is presented. We also use
the algorithm data to find out what kind of patterns the user behavior
follow by examining the resources they devote to our experiment, and
try to fit them to some statistical distribution to create the bases
of a model of user behavior in volunteer computing experiments of this
kind that can be used by researchers to predict its performance. 
In general, our experiments prove, first, that NodIO is a flexible and
low-overhead platform to perform distributed computation experiments
that include volunteers, and then that user behavior follows some patterns,
and, thus, are amenable to a model.
\end{abstract}
